Towards Comparable Active Learning

### 2023-02-03 doc/al_benchmark_paper.tex
meta data
upper bound

@@

\subsection{State Space}
Since every AL agent needs a different state space our environment exposes a callback-function that gives the agent full control over how the state is constructed. \\ [1mm]
The callback includes the following information:
\begin{itemize}
	\item The current sample of IDs that point to the presented unlabeled datapoints
	\item The entire labeled dataset $\mathcal{L}$
	\item The entire unlabeled dataset $\mathcal{U}$
	\item A histogram of labeled points per class (simple count)
	\item The current classification model including all model weights
	\item The current optimizer including it's full state
\end{itemize}
Every agent needs to implement this callback that transforms the given information into a state tensor that will be directly consumed by the agent to make it's prediction.

>>>>

\subsection{Problem Description}
We assume a dataset $\mathcal{D}$ consisting of a large pool of unlabeled data $\mathcal{U}$ and a small set of labeled data called the seed set $\mathcal{S}$: $\mathcal{D} := (\mathcal{U}, \mathcal{S}); \hspace{2mm} |\mathcal{S}| \ll |\mathcal{U|}$. 
For the purpose of this work, only fully labeled datasets are used and the labels for $\mathcal{U}$ are suppressed until they are selected for labeling.
We consider only classification problems, hence the instances of a dataset have the form $x \in \mathbb{R}^M$ for $\mathcal{U}$ and $(x, y) \in (\mathbb{R}^M, \mathbb{R}^C)$ for $\mathcal{S}$.
To perform classification, a model $\phi_\theta := \mathbb{R}^M \rightarrow \mathbb{R}^C$ is used. To fit the model, it is parameterized by $\theta$ and subjected to loss $l(y, \phi_\theta(x)) := \mathbb{R}^C \times \mathbb{R}^C \rightarrow \mathbb{R}$. For this work, categorical cross-entropy (CE) is used.

@@

\subsection{State Space}
Since every AL agent needs a different state space our environment exposes a callback-function that gives the agent full control over how the state is constructed. \\ [1mm]
The callback includes the following information:
\begin{itemize}
	\item The current sample of IDs that point to the presented unlabeled datapoints
	\item The entire labeled dataset $\mathcal{L}$
	\item The entire unlabeled dataset $\mathcal{U}$
	\item A histogram of labeled points per class (count)
	\item The available budget
	\item Number of added datapoints $|\mathcal{L}| - |\mathcal{S}|$
	\item The initial validation accuracy and current validation accuracy
	\item The current classification model including all model weights
	\item The current optimizer including it's full state
\end{itemize}
Every agent needs to implement this callback that transforms the given information into a state tensor that will be directly consumed by the agent to make it's prediction.
